---
output:
  bookdown::pdf_document2:
    toc: false
    number_sections: false
documentclass: article
geometry: margin=0.95in
---

# \textit{Week 6 Report}
\vspace{-2mm}
Ella Hagopian

```{r, include = F}
## Set libraries
library(ggplot2)    ## 3.5.1
library(dplyr)      ## 1.1.4
library(kableExtra) ## 1.3.4
library(readr)      ## 2.1.5

## Read in data
df <- read.csv("../DataRaw/lead-iq-01.csv")

## From 'meeting' with PI: change IQ 999 to 99
df$IQ = ifelse(df$IQ == 999, 99, df$IQ)
```

This project uses data from the CDC and includes two variables: distance from lead smelter to the subject's home (near = $\leq$ 1 mile, far = > 1 mile) and IQ score. **Figure 1** depicts the distributions of IQ scores for those living near and those living far from the smelter. The group living further from the smelter has a higher average IQ than those living near the smelter.

```{r, message = F, fig.cap = "Distribution of IQ score by distance from lead smelter", echo=F}
## Graph of IQ by location status
ggplot(df, aes(x = Smelter, y = IQ)) +
  geom_boxplot() +
  labs(x = "Smelter distance", y = "IQ")
```

**Table 1** presents summary statistics of IQ scores by proximity to the lead smelter. Those living near the smelter had a mean IQ of `r round(with(df[df$Smelter=="Near",], mean(IQ)),2)` (SD: `r round(with(df[df$Smelter=="Near",], sd(IQ)),2)`) and those living far had a mean IQ of `r round(with(df[df$Smelter=="Far",], mean(IQ)),2)` (SD: `r round(with(df[df$Smelter=="Far",], sd(IQ)),2)`).

```{r, echo=F}
## Nicely formatted table
df %>% 
  group_by(Smelter) %>% 
  summarise(n = n(),
            mean = round(mean(IQ),2),
            median = median(IQ),
            sd = round(sd(IQ),2)) %>% 
  kable(col.names = c("Smelter location", "n", "Mean", "Median", "SD"),
        align = c("lcccc"),
        caption = "Summary statistics of IQ scores by proximity to lead smelter"
        ) %>% 
  row_spec(0, bold = T) %>% 
  kable_styling(latex_options = "HOLD_position")
```

